Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2016-10-23 paper.tex
update

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. An optimisation problem is another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimising composition solution. This paper develops a more applicable approach for comprehensive quality in semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. And several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of several web services to provide a value --- added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual service and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

@@

Existing works on service composition are often addressed regarding the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts at the semantic level of web service composition. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match matching as web service composition solution. For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.

@@

\begin{enumerate}
 \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality integrated with QoS --- a more general and applicable evaluation model utilising semantic information of web services in this paper.

 \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration in comprehensive quality, and this service queue is decoded using graph building algorithm to generate optimised comprehensive quality awareness   composite solution.

 \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness utilising the benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are composed as the following: Sect. \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect. \ref{qswsc_approach} represents the an Introduction of of semantic automated web service composition approach, and the comprehensive quality evaluation model; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of these experiments; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to a statement of user's functional requirement; another nonfunctional part specifies the acceptable composite quality of service. To accomplish the composte goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated $T_{Input}$ with found services output, which is used to further discovery more related services until the desired $T_{Output}$ found. It normally results in more than one solutions. Service selection is to select one of those composite solution considering closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach},

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service matching process is to pair the two services' output and input concepts according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.

@@

Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper. Therefore, these three robust and valid matches will be used to discover web service candidates for a service composition.

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS optimisation, which covers aspects in non-functional requirements. This problem have been explored in both single objective and multi-objectives optimisation. Ideally, customers prefer lowest execution cost with highest response time and reliability. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}. Here we consider two composite constructs: both sequence and parallel construts are used in building the composite flow, which are described as follows:

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Figure \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the service composite solution. This construct is presented in Figure \ref{parallel}.

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking. Since semantic descriptions are introduced into web service, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}. In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting in a taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, when $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}. And Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are also required to be pre-calculated in Formula \ref{equation2}. They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

@@

However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined DL in the knowledge representation system. for example, both service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2 are needed. This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method. Therefore, we introduce a more applicable comprehensive quality model in a full automated semantic web service composition.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition. However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the data requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO based approach, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is the users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that is used by PSO as a searching space. Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking, where web services are discovered and connected with calculation of matchmaking quality, which will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web service is performed over the PSO in subSect. \ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for a graph building. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services. In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies. The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

@@

The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}. The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}. The advantage of utilising semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a semantic matchmaking model to evaluate the semantic quality of two matched web services, this fill the gaps in subsection \ref{relatedWork} of current prevailing QoS-aware optimisation, where quality of matchmaking for service selection are not considered.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types, which is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}. Match type is considered to be one factor for the semantic quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the output and input of a request for selecting web services with close semantic matching. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.

\begin{equation}
\label{equation4}
q_{smq} \stackrel{.}{=} (q(s_ {matchType}), \  q(s_ {similarity}))
\end{equation}

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite web services. The non-functional properties typically refer previously discussed QoS, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{smq})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.

\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (q(s_ {smq}), \  q(s_ {QoS}))
\end{equation}
\begin{equation}
\label{equation6}
q_{cq} \stackrel{.}{=} (q(s_ {mt}), \  q(s_ {s}), \  q(s_{a}),\  q(s_{r}),\  q(s_{c}),\  q(s_{t}))
\end{equation}

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Typically, web services could have more than one concept-related parameters. Regarding semantic matchmaking part, edge-level quality aggregation is determined by the mean of concept-related parameter quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edge-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition. Semantic matchmaking aggregation considers two different factor aggregations: the matching type quality aggregation is calculated by the product function of involved edge-level matching type value, and the similarity quality average value of all edge-level similarity quality. The nonfunctional (QoS) aggregation calculation is same to \cite{cardoso2004quality}.

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised ranging from 0 to 1 so that the overall result falls within 0 to 1. Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.

>>>>

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. An optimisation problem is another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems. This paper develops a more applicable approach for comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. And several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

@@

Existing works on service composition are often addressed regarding the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts by the semantic level of web service composition. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match making as web service composition solutions. For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.

@@

\begin{enumerate}
 \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality approach with QoS. This approach is consider to be a more general and applicable way of finding an optimised solution in semantic web service composition.

 \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate optimised comprehensive quality awareness solution.

 \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are composed as the following: Sect. \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect. \ref{qswsc_approach} represents the an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and the whole implementation algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of these experiments; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable composite quality of service. To accomplish the composte goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated a output set: $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$ with found services output. The Output Set is used to further discovery all related services until the desired $T_{Output}$ found in the updated Output Set. It normally results in more than one solutions. Service selection is to select one of those composite solution considering closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach},

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service matching process is to pair the output and input concepts of two services according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ are defined in.

@@

Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper. Therefore, these three robust matches will be used to discover web service candidates for service composition.

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS, which covers aspects in non-functional requirements. This problem have been explored in both single objective and multi-objectives optimisation. Ideally, customers prefer lowest execution cost with highest response time and reliability. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}. Here we consider two composite constructs: both sequence and parallel construts are used in building the composite flow, which are described as follows:

@@

\subsubsection{Sequence construct}
The composite web service executes each atomic service associated with a sequence construct in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Figure \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed in the meantime. The QoS aggregation value in total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is delimited by the maximum time consumed path in the composite flow of the solution. This construct is presented in Figure \ref{parallel}.

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.

In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting in a taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, when $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, the auther utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

@@

However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in the knowledge representation system. for example, we may need service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2. This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected with calculation of matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web service is performed over the PSO in subSect. \ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for building a graph. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services. In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

@@

The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}. The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}. The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.

\subsection{Comprehensive quality model and aggregation matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition, this overcome the disadvantages of current prevailing QoS-aware optimisation, in which quality of matchmaking for service selection are not considered.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}. Match type is considered to be one factor for the semantic quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the given output and available input for selecting web services with close semantic matching. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Formula \ref{equation4}, where the value of $q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) while $q(s_ {similarity})$ is calculated utilising formula \ref{equation1} in subsection \ref{relatedWork}.

\begin{equation}
\label{equation4}
q_{sm} \stackrel{.}{=} (q(s_ {matchType}), \  q(s_ {similarity}))
\end{equation}

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional requirements of composite goal. The non-functional properties typically refer previously discussed QoS, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality $q(s_{smq})$ in Formula \ref{equation5}, which could be further broken down into Formula \ref{equation6}.

\begin{equation}
\label{equation5}
q_{cq} \stackrel{.}{=} (q(s_ {sm}), \  q(s_ {QoS}))
\end{equation}
\begin{equation}
\label{equation6}
q_{cq} \stackrel{.}{=} (q(s_ {mt}), \  q(s_ {s}), \  q(s_{a}),\  q(s_{r}),\  q(s_{c}),\  q(s_{t}))
\end{equation}

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Generally, web services could have more than one concept-related parameters. In semantic matchmaking process, two levels of quality aggregation are considered --- edge level and construct level. At edge level, the edge-level quality aggregation is determined by the mean of concept-related parameter quality in both $q(s_{mt})$ and $q(s_{s})$ respectively. Meanwhile, the construct-level quality is further calculated based on the constructs following the rules in Table \ref{table1}, which is a quality aggregate matrix for semantic web service composition. Both the $Q(s_{mt})$ and $Q(s_{s})$ are considered by calculating the product function of involved edge-level $q(s_{mt})$, and $q(s_{s})$ respectively. The QoS aggregation $Q(q_{QoS})$ calculation is same to \cite{cardoso2004quality}.

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value result falls within 0 to 1. Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.
